How to Name a Real-World Object, and how not to

### 2019-12-06 papers/ACL2020/acl2020_main.tex
[ACL2020] main
[ACL2020] moves bird-duck example to intro
[ACL2020] starts filling in experiments.tex

\title{How to Name a Real-World Object, and how not}

@@

%\appendix
%
\section{Appendices}
\label{sec:appendix}
Appendices are material that can be read, and include lemmas, formulas, proofs, and tables that are not critical to the reading and understanding of the paper.
Appendices should be \textbf{uploaded as supplementary material} when submitting the paper for review.
Upon acceptance, the appendices come after the references, as shown here.

\paragraph{\LaTeX-specific details:}
Use {\small\verb|\appendix|} before any appendix section to switch the section numbering over to letters.

\section{Supplemental Material}
\label{sec:supplemental}
Supplementary material may report preprocessing decisions, model parameters, and other details necessary for the replication of the experiments reported in the paper.
Seemingly small preprocessing decisions can sometimes make a large difference in performance, so it is crucial to record such decisions to precisely characterize state-of-the-art methods.

>>>>

% Terms that need to be replaced throughout the paper by more appropriate ones:
\newcommand{\arbitrary}{arbitrary$_{SIC}$\xspace}

\title{How to Name a Real-World Object, and how not to}

@@

%\appendix
%
\section{Appendices}
\label{sec:appendix}
\iffalse
Appendices are material that can be read, and include lemmas, formulas, proofs, and tables that are not critical to the reading and understanding of the paper.
Appendices should be \textbf{uploaded as supplementary material} when submitting the paper for review.
Upon acceptance, the appendices come after the references, as shown here.

\paragraph{\LaTeX-specific details:}
Use {\small\verb|\appendix|} before any appendix section to switch the section numbering over to letters.
\fi

\section{Supplemental Material}
\label{sec:supplemental}
\iffalse
Supplementary material may report preprocessing decisions, model parameters, and other details necessary for the replication of the experiments reported in the paper.
Seemingly small preprocessing decisions can sometimes make a large difference in performance, so it is crucial to record such decisions to precisely characterize state-of-the-art methods.
\fi

### 2019-12-06 papers/ACL2020/experiments.tex
[ACL2020] starts filling in experiments.tex

@@

We propose to use datasets of object names for evaluating models on the task of object naming (depending on results: also valuable for comparing object detection/image classification models).
Specifically, we analyse object detection [and classification] models on the task of human object naming, using the \mn dataset as test data:\\
Can object detection models, trained on arbitrary names, account for human object naming?
\begin{itemize}
	\item Do they predict the entry-level name?
	\item Are valid name alternatives among the top-N predictions?
	\item Do models make similar mistakes as humans when being faced with the task of naming highlighted objects in images [i.e.,\ the artificial setup of object naming for data annotation]?\\
	-- naming an alternative object (maybe more salient)\\
	-- predicting a semantically related name
	%do we get different evaluation results when testing existing object classification models on preferred responses from name distributions, as compared to naming responses collected from 1-3 workers (e.g., VisualGenome)? 
	\item Can we use \mn as fine-tuning dataset? (Here: only Vanilla model)\\
	-- can we learn entry-level names by fine-tuning object detection models on \mn?\\
	-- Can we directly learn entry-level names by fine-tuning image classification models on \mn, i.e.,\ the pre-trained features to initialize object detection models?
\end{itemize}

@@

\end{tabular}
\caption{Break-down of the results (in \%) according to the agreement level of the MN name: Categorization of a predicted name\ $\hat{n}$ into either a \textit{hit}, \textit{correct} (less preferred name, synonym, hypernym/hyponym), or \textit{wrong} \label{tab:errors_agreement}}
\end{table*}

@@

>>>>

\cs{todo: discuss differences between domains}

Our goal is to experimentally obtain insights into the usefulness of computer vision object labeling models, that are commonly used for \lv methods, to account for natural human object naming. 
Specifically, our research questions are
\begin{enumerate}
	\item Do object detection models, despite being trained on \arbitrary  
	names, account for human object naming?\cs{repetitive}
	\item Can image features, that were pre-trained using object detection or image classification model, be fine-tuned on \mn towards this naming task through simple transfer learning? Figure~\ref{fig:exp_confusions} \\
	\cs{move to models: -- can we learn entry-level names by fine-tuning object detection models on \mn?\\
		-- Can we directly learn entry-level names by fine-tuning image classification models on \mn, i.e.,\ the pre-trained features to initialize object detection models?}
\end{enumerate}
TO BE COVERED BY THE SUBSECTIONS BELOW:
\begin{enumerate}
	\item Do models prefer the entry-level name of an object over an \cs{arbitrary$\rightarrow$?} name? Table~\ref{tab:exp_VGvsMN}
	\item In cases of failure, do they predict alternative, but less preferred  names instead? Tables~\ref{tab:exp_overview_results}, \ref{tab:exp_alternatives}
	\item What phenomena of human behavior on the object naming task of \mn do the models mirror? That is, which model mistakes or confusions are due to the artificial setup of the task itself, and less a failure of the model? (Recall that \mn serves as a \textit{proxy} for natural human object naming, since annotators were asked to name a highlighted object in an image isolated from its situative context; Section~\ref{sec:manynames}) Table~\ref{tab:exp_details_wrong} (and \ref{tab:exp_errors_agreement},  \ref{tab:exp_alternatives})

	%That is, do they make similar mistakes (wrong object--maybe more salient?, related name, e.g.,~co-hyponyms)?
	\item \cs{Not examined at the moment -- MRR and Jaccard may be re-added for this: Are valid name alternatives among the top-N predictions?}
	%\item do we get different evaluation results when testing existing object classification models on preferred responses from name distributions, as compared to naming responses collected from 1-3 workers (e.g., VisualGenome)? 
\end{enumerate}
We use the \mn dataset in two ways, as analytical testbed, and for fine-tuning pre-trained image features towards entry-level name prediction.

\paragraph{Models}
We test two object detection models that are trained with a different vocabulary:

\subsection{Results}
\label{sect:exp_results}

\paragraph{Entry-Level Name Prediction}

\begin{table}[t]
	\centering
	\small
	\begin{tabular}{l@{~}|@{~}c@{~}|@{~}r@{~}r@{~}|@{~}r@{~}r@{~}}
		\toprule
		&  & \multicolumn{2}{c}{All} 
		& \multicolumn{2}{c}{VG$\neq$MN}\\
		&  & \multicolumn{2}{c}{($1072$)} 
		& \multicolumn{2}{c}{($223$)}\\	
		Model--Vocab	 
		&  GTtrain &  =VG & =MN 
		&  =VG & =MN \\ 
		\midrule
		FRCNN--MN442 & VG &  65.4 &      71.2 &   20.0 &      48.4  \\
		FRCNN--VG1600 & VG &    67.3 &      74.5 &    19.1 &      52.9  \\
		\midrule \midrule
		\multicolumn{6}{c}{Classifiers: Fine-tuning pre-trained features on MN}\\
		Features--Vocab &   \\
		\midrule 
		FRCNN--VG1600--VGMN & MN &    70.8 &      80.6 &    13.8 &      60.4  \\ 
		\midrule
		ResNet101--VGMN & MN  & 60.9 &  68.6 &  13.8 & 50.2  \\

		ResNet101--MN442 & MN &            61.7 &              69.6 &                        13.8 &              50.7 \\
		ResNet101--VGMN\_4ep  &   VG &  62.4 &              62.9 &              28.4 &              31.1  \\
		ResNet101--VGMN\_8ep & VG &            63.9 &              62.6 &          34.2 &              28.0 \\
		ResNet101--MN442 & VG  &            63.7 &              63.7 &                  30.7 &              31.1  \\
		\bottomrule
	\end{tabular}
	\caption{Target vocabulary in test data: MN442. Vocab denotes the dataset from which the target vocabulary for training was induced (the numbers give the size of the vocabulary). GTtrain denotes the dataset from which the ground truth labels are obtained during \textit{training}. Note that we considered all name responses in MN, including those with $\text{count}(name)<2$\label{tab:exp_VGvsMN}. }
\end{table}

\paragraph{Alternative Name Prediction}
\begin{figure}
	\centering
	\includegraphics[scale=.2]{images/2323938.jpg}
	\includegraphics[scale=.2]{images/2322259.jpg}
	\includegraphics[scale=.2]{images/2371657.jpg}

	\caption{TODO: examples resnet mistakes (trained on vg\_manynames, tested on manynames-442)\label{fig:mistakes}}
\end{figure}

\cs{TODO::}
Categorization of "errors" (see Figure~\ref{fig:mistakes}):
\begin{enumerate}
	\item Clear mistake \\
	e.g.,\ rice vs. bread
	\item Alternative name\\
	e.g.,\ building vs. house
	\item Alternative object \cs{(other cluster from verif data)}
	\item Synonym\\
	e.g.,\ plane vs. airplane
	\item Semantically related\\
	e.g.,\  motorcycle vs. scooter
\end{enumerate}

	\end{tabular}
	\caption{Break-down of the results (in \%) according to the agreement level of the MN name: Categorization of a predicted name\ $\hat{n}$ into either a \textit{hit}, \textit{correct} (less preferred name, synonym, hypernym/hyponym), or \textit{wrong} \label{tab:exp_errors_agreement}}
\end{table*}

	\caption{Break-down of the results for the \textit{correct} name predictions. Proportions (in \%) of the \textit{correct} categories to all correctly classified instances.  \textit{hyponym}: $\hat{n}$ is a hyponym of the entry-level name. \textit{hypernym\_cl}: $\hat{n}$ is a hypernym of any of the valid names (cluster). \textit{Synonym} and \textit{synonym\_cl} are analogous. \label{tab:exp_alternatives}}
\end{table*}

\paragraph{Incorrect Predictions}

\paragraph{Human Object Naming through Transfer-Learning} Figure \ref{fig:exp_confusions} visualizes the change in predictions for  some of our retrained and finetuned models with respect to the object detection baseline (bottom-up-1600). For each object, where the new model predicts a different name than the baseline model, we look at the hit-error categories of the original and new predicted name. Observations:
\begin{itemize}
	\item Retraining faster-rcnn on less names does not lead to better calibration of entry-level names: more original hits change to same-cluster predictions than the other way round. (top left matrix)
	\item Finetuning the original faster-rcnn on many names recalibrates many decision from same-cluster names to the correct hit. Interestingly, also clear errors are calibrated to perfect hits, whereas hardly any error is changed to same-cluster or related.  (top right matrix)
	\item A similar tendency can be found for the ResNet models: finetuning ResNet on MN changes many predictions from same-cluster to hits. This is less the case when ResNet is finetuned on VG annotations.
	\item Interestingly, both ResNet models change hits into related names (hypernyms, hyponyms, cp-hyponyms) -- why does this happen?
\end{itemize}

	\caption{Confusion-matrix-style visualization showing error categories of predictions that changed from object detection with FRCNN-VG1600 to naming with FRCNN-VG1600-VGMN (finetuned) \label{fig:exp_confusions}}
\end{figure*}

\subsection{Discussion}
\label{sect:exp_discussion}

@@

\iffalse
We propose to use datasets of object names for evaluating models on the task of object naming (depending on results: also valuable for comparing object detection/image classification models).
Specifically, we analyse object detection [and classification] models on the task of human object naming, using the \mn dataset as test data:\\
Can object detection models, trained on arbitrary names, account for human object naming?
\begin{itemize}
	\item Do they predict the entry-level name?
	\item Are valid name alternatives among the top-N predictions?
	\item Do models make similar mistakes as humans when being faced with the task of naming highlighted objects in images [i.e.,\ the artificial setup of object naming for data annotation]?\\
	-- naming an alternative object (maybe more salient)\\
	-- predicting a semantically related name
	%do we get different evaluation results when testing existing object classification models on preferred responses from name distributions, as compared to naming responses collected from 1-3 workers (e.g., VisualGenome)? 
	\item Can we use \mn as fine-tuning dataset? (Here: only Vanilla model)\\
	-- can we learn entry-level names by fine-tuning object detection models on \mn?\\
	-- Can we directly learn entry-level names by fine-tuning image classification models on \mn, i.e.,\ the pre-trained features to initialize object detection models?
\end{itemize}

@@

\end{tabular}
\caption{Break-down of the results (in \%) according to the agreement level of the MN name: Categorization of a predicted name\ $\hat{n}$ into either a \textit{hit}, \textit{correct} (less preferred name, synonym, hypernym/hyponym), or \textit{wrong} \label{tab:exp_errors_agreement}}
\end{table*}

@@

\fi
